% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage[colorlinks = true,
linkcolor = blue,
urlcolor  = blue,
citecolor = blue,
anchorcolor = blue]{hyperref}
\usepackage{fontawesome}
\usepackage[left=1cm, right=2cm, top=1cm,bottom = 5 mm ]{geometry}

\begin{document} 
	
\name{Saad Amien Hassan\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{\bf  Conact Info\\+02 01007484458\\ {\url{saad.amien.hassan@gmail.com}}}
\address{\bf Address \\Giza, Egypt \\  \faLinkedin \hspace{0.10em}  {\href{https://www.linkedin.com/in/saad-amien/}{Saad-Amien}}\\
	\faGithub \hspace{0.10em} 
         \href{https://github.com/SaadAmien20}{SaadAmien}}                       
\begin{resume}
	\vspace{-0.1in}

\section{Summary} 
\vspace{1.3 mm} 

   Experienced with ETL Process, knowledge with building data warehouse, and +3 years’ experience in data management, skilled in MSBI (SQL Server Integration Services, SQL Server Reporting services), IBM Infosphere DataStage, Hadoop ecosystem, Big Data Analytics, and Apache Spark, Python, skilled in data visualization with Power bi and OBIEE .       

\section{WORK EXPERIENCE}
\vspace{2 mm } 
\textbf{Data Engineer/ Data Modeler, VodafoneEgypt}
\quad \quad  \quad \quad \quad \quad \quad \quad \quad \quad \quad 
\quad \quad \quad\quad \quad \quad \quad \quad \quad\textbf{Dec 2019-Present} 
 \vspace{2 mm } 
\begin{itemize}
	\setlength\itemsep{0.001 em}
	\item Analyze business requirements and designed solutions for Data Warehouse and Analytics projects.
	\item Building models and making ETL jobs to load data from multiple sources to those models.
	\item  Building a data warehouse to enable analytics , data science, and machine learning , tune and run the data platform end-to-end.
	\item using patterns to Secure customers data from unrelated persons using pandas  and numpy libraries.	
	\item Cloud Technologies: Azure.
\end{itemize} 

\vspace{1 mm } 
\textbf{Data Engineer/ BI developer, Master-Works}
\quad \quad  \quad \quad \quad \quad \quad \quad \quad \quad \quad 
\quad \quad \quad\quad \quad \quad \quad \quad \quad\ \quad \textbf{Jun 2018-Dec 2019} 
\vspace{-02 mm}
\begin{itemize}
\item Build Packages with SSIS and Pipelines with Azure Data Factory to load Data from Multiple Data Sources to DW according to The DDM file.
\item Design \& develop Dashboards using Power bi, OBIEE.
\item Design reports using SSRS.
\item Responsible for the production and maintenance of standard analytics and reports.
\item Validation of Data Integrity as a part of quality control
\end{itemize} 
\textbf{Projects:} 
\vspace{2 mm } 
\begin{itemize}
	\item \textbf{Building Quality gate for Dw} Establishing Quality Gate for Data Warehouse for checking trend analysis to helping Marketing
	Insights with sending mail if it breaks the threshold and helping the support team to check Business rules
	and differences in rows between sources and destinations by sending mail to them if there are issues.
	\item \textbf{Design Data Warehouse and ETL for Dur Hospitality Company using Azure}
	Description: Design modeling For Data Warehouse and choose what Schema will apply
	whether Star and snowflake schema and Making Extraction and transformation to data sources
	Using Azure Data Factory.
	\item \textbf{Design Data Warehouse and ETL for Dur Hospitality Company using Azure}
	Description: Design modeling For Data Warehouse and choose what Schema will apply
	whether Star and snowflake schema and Making Extraction and transformation to data sources
	Using Azure Data Factory.
\end{itemize}
\section{EDUCATION}          
    B.Sc of Science in Computer Science, Faculty of Computers \quad \quad
    \quad \quad  
    \quad \quad \quad \quad \quad \quad \quad 
    \quad \quad \quad \quad \quad \quad \quad \quad  \textbf{2012 - 2016} \\
    and Information Systems, Helwan University         

\section{Technical Skills}          
  \textbf {Languages and Technologies:} \vspace{2 mm } 
  \begin{itemize}
  	\item DBMS: Oracle, Microsoft SQL,PostgreSQL, MySQL.
  	\item Enterprise ETL Tools: IBM Data Stage, SSIS,Azure Data Factory.
  	\item Python, C++, Shell Programming, Latex.
  	\item Big Data Development (Hadoop, Spark, Pig, Hive, Nifi and Airflow).
  	\item Data visualization \& reporting tools:Power Bi, SSRS
  \end{itemize}     
 
\section{Certifications}          
   \begin{itemize}
   	\item \href{https://www.coursera.org/specializations/big-data}{Big Data Specialization (3 Courses Specialization)} , By University of California, San Diego
   	\item \href{https://www.coursera.org/learn/python-project-for-data-engineering/home/welcome}{Python Project for Data Engineering} by IBM
   	\item \href{https://www.coursera.org/learn/python-network-data/home/welcome}{Using Python to Access Web Data} by UNIVERSITY OF MICHIGAN
   \end{itemize}      
 
\end{resume}
\end{document}
